---
title: "Final Report: Your Title Here"
author: "Leila Esmaeili"
date: "December 5, 2018"
output:
    github_document: default
bibliography: references.bib
csl: bioinformatics.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Add about 2-3 pages here. Across the whole manuscript, you should cite at least 20 peer reviewed articles.

# Methods

## Study design

Add about half a page here. In this section instead of first person (I/we), use the authors of the paper you selected, since you'll just be describing what they did, based on the methods in their paper.

## Sample origin and sequencing

Add about half a page here. In this section instead of first person (I/we), use the authors of the paper you selected, since you'll just be describing what they did, based on the methods in their paper.

## Computational

These are the methods you used to do your bioinformatic analyses analyses. Should probably be between 0.5 and 1 pages. At a very minimum should include citations for DADA2 and phyloseq if you are doing an amplicon study, or other citations as appropriate.

# Results

## Subsections are ok in the results section too

```{r your-code-here}
# Add code chunks as needed for your analyses
# For most analyses, I would recommend splitting the
# intensive computational part into a seperate R script file
# and then just load your libraries and the data object here
# using the `load()` function. Ask me for clarification if this is
# unclear.
```

```{r load-packages-and-data}
# load packages as needed
library("dplyr")
library("knitr")

# load data produced from analysis scripts using
load("output/phyloseq_obj.Rdata")
load("output/melted_phyloseq.Rdata")
```

```{r example-table}
melted_phyloseq %>%
  group_by(host_age) %>%
  summarize(mean_abund = mean(Abundance)) %>%
  kable()
```

```{r abundance-across-age-groups}
# bar plot of age group and Abundance of sequences to visualize
# total abundance in each of the 3 unique age groups
plot_bar(phyloseq_obj, x = "host_age")
```

**Figure 1** This graph is a histogram that shows Abundance of seqences across 
age groups. The largest number of  sequences was seen in Adults.  


```{r histogram-diversity-Adolescent}
# Abundance of  sequenecs in age group T to visualize diversity across classes
age_phyloseq_obj <- subset_samples(phyloseq_obj, host_age == "adolescent (T)")
plot_bar(age_phyloseq_obj, x = "Class")
```

** Figure 2** This graph is a histogram that describes diversity of classes in 
Adolecents

```{r histogram-diversity-Adults}
# Histogram abundace Adults to visiualize diversity across classes
age_phyloseq_obj <- subset_samples(phyloseq_obj, host_age == "adult (A)")
plot_bar(age_phyloseq_obj, x = "Class")
```

** Figure 3** 
This graph is a histogram that describes the abundance of sequences
found in Adults  


```{r histogram-diversity-Elderly}
# Histogram abundance  Elderly to visualize diversity across classes
age_phyloseq_obj <- subset_samples(phyloseq_obj, host_age == "elderly (O)")
plot_bar(age_phyloseq_obj, x = "Class")
```


** Figure 4** This graph is a histogram that describes the abundance of 
sequences found in Elderly

In addition to a minimum of 5-8 figures/tables (and associated captions), you should include sufficient text in this section to describe what your findings were. Remember that in the results section you just describe what you found, but you don't interpret it - that happens in the discussion. 2-3 pages.

# Discussion

Add around 3-4 pages interpreting your results and considering future directions one might take in analyzing these data.

# Sources Cited
